ABC inferences

### 2024-12-16 application_examples/abc_inferences/draft-abc-inferences-vignette.Rmd
Updating changes in location of abc_inferences workflow

```{bash, eval = FALSE}
Conda must be version 24.7.1 or later, found version 22.11.1. Please update conda to the latest version. Note that you can also install conda into the snakemake environment without modifying your main conda installation.
# Then I installed conda into the snakemake environment with
conda activate abc_inferences
conda install -c conda-forge conda 
```

>>>>

```{bash, eval = FALSE}
Conda must be version 24.7.1 or later, found version 22.11.1. Please update conda to the latest version. Note that you can also install conda into the snakemake environment without modifying your main conda installation.
# Then I tried to install conda into the snakemake environment with
conda activate abc_inferences
(abc_inferences) saracv@australia:~/MasterThesis/MethEvolSIM/extensive_tests/abc_inferences$ conda install conda=24.11.0                                                                                                                      
Collecting package metadata (current_repodata.json): done                                                                                                                                                                                 
Solving environment: done                                                                                                                                                                                                              
==> WARNING: A newer version of conda exists. <==                                                                                                                          
  current version: 22.11.1                                                                                                               
  latest version: 24.11.0                                                                                                                                                                                                     
Please update conda by running                                                                                                                                                                                                           
    $ conda update -n base -c conda-forge conda                                                                                                                                                                                          
Or to minimize the number of packages updated during conda update use                                                                                                                                                                         
     conda install conda=24.11.0

# All requested packages already installed.

(abc_inferences) saracv@australia:~/MasterThesis/MethEvolSIM/extensive_tests/abc_inferences$ conda --version
conda 22.11.1

**This does not seem to work. I tried it out with**:

```{bash, eval = FALSE}
conda activate snakemake
nohup nice snakemake --use-conda run_sim > run_sim.out &
```

and seems to be stuck in:

```{bash, eval = FALSE}
cat run_sim.out 
Injecting conda environment /home/saracv/MasterThesis/MethEvolSIM/extensive_tests/abc_inferences/environment.yaml.
```
